---
title: "Assignment04 - Vizualization of Diversity and Inclusion in the Workplace"
author: "Maria Pachon"
date: "September 27th, 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#set up packages
library(tidyverse)

#loads data
#data <- read_csv("FEVS_2019.csv")
```

## Overview
For this analysis, I will be using the 2019 Federal Employee Viewpoint Survey (FEVS). This is a survey which provides employee's perceptions on the work environment and the overall success in their work unit. The survey also has a number of demographic measures that provide insight into how these perspectives may converge or diverge across groups. The FEVS has been used to create  a number of tools focused on diversity and inclusion in the work place.
The FEVS data is public and available here: [RStudio] (https://www.opm.gov/fevs/public-data-file/)

```{r }
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
