---
title: "Assignment04 - Vizualizing Diversity and Inclusion in the Workplace"
author: "Maria Pachon"
date: "September 27th, 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#set up packages
library(tidyverse)
install.packages("ggridges")
##add github url

```

## Overview
For this analysis, I will be using the 2019 Federal Employee Viewpoint Survey (FEVS). This is a survey which provides employee's perceptions on the work environment and the overall success in their work unit. The survey also has a number of demographic measures that provide insight into how these perspectives may converge or diverge across groups. The FEVS has been used to create  a number of tools focused on diversity and inclusion in the work place.
The FEVS data is public and available here: [RStudio] (https://www.opm.gov/fevs/public-data-file/)

```{r ,include=FALSE}
#loads data
dta <- read_csv("FEVS_2019.csv")
#transforms data into tibble
dta <- as_tibble(dta)

#transforms Q30 from character to numberic
dta1 <- dta %>%
  mutate(Q30 = as.numeric(Q30)) %>%
  group_by(Q30, DMINORITY) %>%
  filter(DMINORITY == "A" | DMINORITY == "B") 
 

agg <- acc %>%
  group_by(StateFIPSCode, YEAR) %>%
  summarize(TOTAL = sum(FATALS))


minority <- dta %>%
  mutate(Q30 = as.numeric(Q30)) %>%
  group_by(DMINORITY, Q30)  %>%
  filter(DMINORITY == "A") 


```

## Plot 1

```{r pressure, echo=FALSE}

#Plot of feeling of empowerment by minority group 
ggplot(data = minority, mapping = aes(x = Q30)) + 
  geom_histogram(bins = 15, fill = "dodgerblue3") +
  scale_x_continuous(expand = expand_scale(mult = c(0, 0.1)), 
                     limits = c(0, 5)) +  
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.2)), labels = scales::comma) +
  labs(x = "Group: Minorities",
       y = "Count") +
  ggtitle("Employees feeling of personal empowerment \n with respect to work processes") +
  theme(plot.title = element_text(hjust = 0.5))

```


## Plot 2
```{r pressure, echo=FALSE}

nonminority <- dta %>%
  mutate(Q30 = as.numeric(Q30)) %>%
  group_by(DMINORITY, Q30)  %>%
  filter(DMINORITY == "B") 


#Plot of feeling of empowerment by minority group 
ggplot(data = nonminority, mapping = aes(x = Q30)) + 
  geom_histogram(bins = 15, fill = "violet") +
  scale_x_continuous(expand = expand_scale(mult = c(0, 0.1)), 
                     limits = c(0, 5)) +  
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.2)), labels = scales::comma) +
  labs(x = "Group: Non-Minorities",
       y = "Count") +
  ggtitle("Employees feeling of personal empowerment \n with respect to work processes") +
  theme(plot.title = element_text(hjust = 0.5))

```

## Plot 3
```{r pressure, echo=FALSE}

dta1 <- dta1 %>%
  mutate(Q34 = as.numeric(Q34))


#creates plot 
ggplot(data = dta1, aes(x = DMINORITY, y = Q34)) +
  geom_bar(stat = "identity", width = 0.5, fill = "dodgerblue3") +
  ggtitle("Employee's perception on the promotion of programs focused on diversity in the workplace") +
       xlab("Group") + ylab("Count") +
      theme(plot.title = element_text(hjust = 0.5))


```

## Plot 4

```{r pressure, echo=FALSE}

nonminority <- dta %>%
  mutate(Q30 = as.numeric(Q30)) %>%
  group_by(DMINORITY, Q30)  %>%
  filter(DMINORITY == "B") 




#Plot of feeling of empowerment by minority group 
ggplot(data = nonminority, mapping = aes(x = Q30)) + 
  geom_histogram(bins = 15, fill = "violet") +
  scale_x_continuous(expand = expand_scale(mult = c(0, 0.1)), 
                     limits = c(0, 5)) +  
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.2)), labels = scales::comma) +
  labs(x = "Group: Non-Minorities",
       y = "Count") +
  ggtitle("Employees feeling of personal empowerment \n with respect to work processes") +
  theme(plot.title = element_text(hjust = 0.5))

```